Supplementary Material for Asymmetry paper

### 2020-05-01 Supplementary/Sup_mat.Rmd
something

# Resampling
For experiments 1, 3, and 4 we made use of resampling existing data as we had run experiments in the past that were comparable. Experiment 2 was slightly different in that we did not have previous data to compare to, as such, we generated a series of distributions based on previous data. Resampling was carried out in order to establish if adding more pariticipants to our sample sizes would have lead to a reduction in uncertainty around our estimates.

## Probability 
For this experiment, data from ($N$ = 12) Clark and Hunt (2016), which acted as a substitute for the Symmetric condition, and an unpublished pilot study ($N$ = 11), which followed the same rules as the Bias condition in the main experiment, were resampled in order to invesigate how often participants would fixate one of the side boxes given it was more likely to contain the target for the Bias condition. For the Symmetric condition, we followed the same rule as the in the paper and classified the most likely box as the side box that participants fixated most often. These data are shown in the box plots of the figure below. The main interest for our purposes was the proportion of time participants fixated the most likely box.

The data were coded so that a fixation was classified as either being to the Most likely box or not. We then resampled (with replacement) these data by selecting a random $N$ participants from each condition (ranging from 2 to 20) then sampling 300 trials from these participants from the different datasets. This was done 5000 times to estimate the expected difference between the Symmetric and Bias conditions in terms of proportion of fixations to the Most likely side and the associated certainty around these values.

As can be seen in the figure below, the uncertainty surrounding the estimate for the difference between the groups appears to plateau somewhere around 15 participants. The shaded region represents a 95% Highest Density Interval (HDI) for the disribution of differences simulated through resampling. As such, the sample size of 18 in the main experiment appears to be ample in order to detect this difference and increasing the sample size above this value does not add more to the certainty.

```{r load data, include = F, echo = F, message = F, warning = F}
load("../power/Prob_match/scratch/df_resample")
load("../power/Prob_match/scratch/df_sample")
```

```{r make plots, include = T, echo = F}
plt_data <- df_resample %>%  
  ungroup() %>% 
  group_by(Participant, Condition, Dist_type) %>% 
  mutate(centre = ifelse(box_type == "Centre", 1, 0),
         ML = ifelse(box_type == "Most", 1, 0),
         LL = ifelse(box_type == "Least", 1, 0),
         n = n()) %>%
  summarise(centre = mean(centre),
            ML = mean(ML),
            LL = mean(LL)) %>% 
  gather(centre:LL,
         key = "prop_type",
         value = "proportion") %>%
  mutate(prop_type = factor(prop_type, c("centre", "ML", "LL"),
                            labels = c("Centre", "Most Likely", "Least Likely"))) %>% 
  ggplot(aes(Dist_type, proportion,
             fill = Condition,
             colour = Condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) +
  facet_wrap(~prop_type) +
  see::scale_color_flat() +
  see::scale_fill_flat() +
  theme_bw() +
  scale_x_discrete("Distance Type") +
  theme(axis.title.y = element_blank())

# maybe just the hdi stuff?
# do I want to rerun the sim with dist type added in?
plt_resampling <- df_sample %>% 
  spread(Condition, 
         Most) %>% 
  mutate(diff = Bias - Symmetric) %>% 
  group_by(n_sub) %>% 
  summarise(mu = mean(diff),
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_sub, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) +
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Differenc in fixations to more \n likely side (Bias - Symmetric)")

gridExtra::grid.arrange(plt_data, plt_resampling)
```

## Hoop Sizes

Resampling for this experiment took the form of fitting a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the fitdistrplus package. The values estimated using this procedure could were then adjusted to look at how reliably different sizes of effects could be detected. We altered the mean value but kept the variance the same to simulate participants shifting in one direction or the other. As can be seen in the figure below, we tested 4 different values (0.05, 0.1, 0.015, and 0.2) which were indicative of participants standing $X$\% closer to one side (in this case, in the direction of the smaller hoop). These ditributions were sampled from 5000 times by simulating $N$ participants (from 3 to 24) and simulating 72 trials. The plot below the distributions shows the uncertainty surrounding the mean estimate for the smallest difference tested (5\%). After 15 participants, the uncertainty surrounding the estimate appears to plateau which demonstrates that the sample size of 21 was sufficient to detect the effect. 
```{r load data and draw distributions, include = T, echo = F}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

# draw these 
df_distributions <- tibble(x_vals = rep(x, length(c(0,mu2))),
                           base = mu1,
                           diff = rep(c(0,mu2), each = length(x)),
                           var = var1,
                           alpha = get_shape_beta(base + diff, var)$alpha,
                           beta = get_shape_beta(base + diff, var)$beta,
                           est_mu = mu_beta(alpha, beta),
                           est_var = var_beta(alpha, beta),
                           p = dbeta(x_vals, alpha, beta))
plt_distributions <- df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p,
             colour = diff)) + 
  geom_line() + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")

plt_hdi <- df_sample %>% 
  filter(difference == 0.05) %>% 
  group_by(n_subs) %>% 
  mutate(diff = comparison - baseline) %>% 
  summarise(mu = mean(diff), 
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) + 
  scale_x_continuous("Sample Size") + 
  theme_bw() + 
  theme(axis.title.y = element_blank())

gridExtra::grid.arrange(plt_distributions, plt_hdi)
```

## Two Throws and Reward
As the hypothesis for both of these experiments was that out intervention would push participants towards being more optimal, we can use the same datasets to look at how uncertainty around the difference would change with varying sample sizes. For these experiments, comparison data was drawn from two unpublished studies; one in which the standard behaviour was observed, and one in which participants were closer to optimal in their performance.

@@

# Analysis

## Probability

```{r Probability, include = F, echo = F}
# Load in everything from the modelling
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt_draws")
draws <- fix_like_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  select(-estimate)
```

```{r Probability show plots, include = T, echo = F, fig.cap = "posterior predictions for the probability matching experiment"}
# this is meant to add a figure caption but it looks terrible
# fig.cap="\\label{fig:fig1}Posterior predictions for the probability matching experiment"}
# Proportion fixations to most likely side 
plt_me_Bias <- draws %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  theme(axis.title.x = element_blank()) +
  labs(fill = "Bias Type",
       colour = "Bias Type") +
  #       "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

plt_me_Dist <- draws %>% 
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() +  
  theme(axis.title.x = element_blank()) +
  labs(fill = "Distance Type",
       colour = "Distance Type") +
  #       x = "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

plt_interaction <- fix_like_post$plt_estimates +
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  labs(x = "Proportion of Fixations to Most Likely Side",
       colour = "Bias Type",
       fill = "Bias Type") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

gridExtra::grid.arrange(plt_me_Dist, plt_me_Bias, plt_interaction)
```

```{r Get Values, include = F, echo = F}
# HDI_values 
HDI_Bias <- draws %>%
  group_by(Bias_type) %>%
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))
HDI_Dist <- draws %>% 
  group_by(Dist_type) %>% 
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))
HDI_interaction <- draws %>% 
  group_by(Bias_type, Dist_type) %>% 
  summarise(lower = hdi(prop)[,1],
            mu = mean(prop),
            upper = hdi(prop)[,2],
            med = median(prop))

# Diff values 
Diff_Bias <- draws %>% 
  spread(Bias_type, 
         prop) %>%
  mutate(diff = Bias - Symmetric,
         Bias_bigger = ifelse(diff > 0, 1, 0))
D_bias_lower <- hdci(Diff_Bias$diff)[,1]
D_bias_mu <- mean(Diff_Bias$diff)
D_bias_upper <- hdci(Diff_Bias$diff)[,2]
p_bias_bigger <- mean(Diff_Bias$Bias_bigger)

Diff_Dist <- draws %>% 
  spread(Dist_type, 
         prop) %>%
  mutate(diff = Far - Close,
         Far_bigger = ifelse(diff > 0, 1, 0))
D_dist_lower <- hdci(Diff_Dist$diff)[,1]
D_dist_mu <- mean(Diff_Dist$diff)
D_dist_upper <- hdci(Diff_Dist$diff)[,2]
p_far_bigger <- mean(Diff_Dist$Far_bigger)

Diff_Interaction_compdist <- Diff_Dist %>% 
  group_by(Bias_type) %>% 
  summarise(p_Far_bigger = mean(Far_bigger),
            lower = hdci(diff)[,1],
            mu = mean(diff),
            upper = hdci(diff)[,2],
            med = median(diff))
Diff_Interaction_compbias <- Diff_Bias %>% 
  group_by(Dist_type) %>% 
  summarise(p_Bias_bigger = mean(Bias_bigger),
            lower = hdci(diff)[,1],
            mu = mean(diff),
            upper = hdci(diff)[,2],
            med = median(diff))

```
The results of this model suggest that our participants were sensitive to the probability information (see above figure). In the Biased condition, the average participant fixated the most likely target `r paste(round(HDI_Bias[1,3], digits = 3)*100, "%", sep = "")` of the time (95% HDPI of |`r paste(round(HDI_Bias[1,2], digits = 3)*100, "%", sep = "")`, `r paste(round(HDI_Bias[1,4], digits = 3)*100, "%", sep = "")`|), compared to `r paste(round(HDI_Bias[2,3], digits = 3)*100, "%", sep = "")` (95% HPDI of |`r paste(round(HDI_Bias[2,2], digits = 3)*100, "%", sep = "")`,`r paste(round(HDI_Bias[2,4], digits = 3)*100, "%", sep = "")`|) in the symmetric condition. The width of these intervals reflects a high degree of uncertainty in fixed effects, due to the range of behaviours exhibited by participants. None-the-less, the HPDI on the difference between these two conditions, |`r round(D_bias_lower, digits = 3)`, `r round(D_bias_upper, digits = 3)`| is largely positive and we can be reasonably confident (P(difference > 0 | data ) =  `r round(p_bias_bigger, digits = 3)`) that the most-likely target is fixated more frequently in the biased condition. The distance between the square targets did not appear to have any consistent effect in the Symmetric condition, however there was a small decrease in fixations towards the “most likely” box when the boxes were far apart in the bias condition (dropping from `r round(HDI_interaction[1,4], digits = 3)`%, 95% HPDI of |`r round(HDI_interaction[1,3], digits = 3)`%,`r round(HDI_interaction[1,5], digits = 3)`%| to `r round(HDI_interaction[2,4], digits = 3)`%, 95% HPDI of |`r round(HDI_interaction[2,3], digits = 3)`%,`r round(HDI_interaction[2,5], digits = 3)`%|). As such, the difference between the conditions were much more pronounced in the close condition (P(Bias > Symmetric|data)) = `r round(Diff_Interaction_compbias[1,2], digits = 3)`%) than in the far condition (P(Bias > Symmetric|data)) = `r round(Diff_Interaction_compbias[2,2], digits = 3)*100`%). The width of these intervals reflects the range of performance that was exhibited by participants. However, this does show that participants generally made us of this probability information in order to decide where to fixate.

```{r model for side fixations, echo = F, include = F}
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_S_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_S_dt_draws")
df_prop_S <- fix_S_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate))
```

```{r plots side fixations, echo = F, include = T}
# something like the first set of plots above 
plt_S_Dist <- df_prop_S %>% 
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) + 
  guides(fill = guide_legend(title = "Distance Type"),
         colour = guide_legend(title = "Distance Type"))

plt_S_Bias <- df_prop_S %>% 
  ggplot(aes(prop, 
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) + 
  guides(fill = guide_legend(title = "Bias Type"),
         colour = guide_legend(title = "Bias Type"))

plt_S_overall <- df_prop_S %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous("Proportion of Fixations to Most Likely Side",
                     labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank()) + 
  guides(fill = guide_legend(title = "Bias Type"),
         colour = guide_legend(title = "Bias Type"))

gridExtra::grid.arrange(plt_S_Dist, plt_S_Bias, plt_S_overall)
```

```{r get HDPI values, echo = F, include = F}
```

We can now ask whether participants were more likely to make use of the optimal strategy when in the biased condition. We will use the same predictors as above, but this time, to predict the probability of participants fixating either of side boxes over the central box. A random observer, equally likely to look at any of the three boxes, would have a 66% chance of fixating a Side box. The results suggest that in the Biased condition, participants were more likely to fixate the side boxes than the central box in both the close (95.4%,HPDI of |85.9%, 99.9%|) and far (96.4%, HPDI of |86.9%, 100%|) conditions. This contrasts with  than when the participants were in the Symmetric condition (close; 83.9%, 95% HPDI of |60.3%, 98.5%|) for the close, and , far; 84.7%,( 95% HPDI of |62.8%, 99.9%|) for the far apart targets in the symmetric condition. These results would suggest that the bias present in the Biased condition encouraged participants to fixate the side boxes more often. However, it does not suggest that adding this bias facilitated the use of the optimal strategy as participants did not appear to account for distance in an optimal manner.

## Hoop Sizes 
```{r Load in Hoop size data, inclued = F, echo = F}
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1")
load("../Analyses/Experiment_3_Hoop_size/modelling/model_outputs/m1_draws")
```

```{r Sort out plots, include = T, echo = F}
plt_estimates <- draws$plt_estimates
plt_estimates
```

```{r Sort Hdis, include = F, echo = F}
p_above_5 <- draws$Prop_above.5
HDI_all <- draws$draws_HDI[[2]]
```

The data from this experiment were analysed using a Bayesian beta regression. The recorded data for standing positions were transformed to be between 0 and 1, with 0 representing the larger hoop and 1 representing the smaller hoop. Therefore, the central point would be 0.,5, and meaning anything above this value would demonstrate a shift in participant’s bhaviour away from the mid-point and towards the small hoop. The model included normalised hoop delta as a predictor to see how participants changed position with an increasing distance. This was also entered as a random effect by participant.

The model results confirmed that participants in general had a bias towards standing closer to the small hoop (mean of `r round(HDI_all$mean, digits = 3)`, 95% HDPI of |`r round(HDI_all$lower, digits = 3)`, `r round(HDI_all$upper, digits = 3)`|). We can be reasonably confident about this results as the p(x > 0.5|data) = `r paste(round(p_above_5$above0_5, digits = 3)*100, "%", sep = "")`. This can be seen in the posterior in the above figure. Also, not that distance did not appear to have an effect on position (i.e., participants were generally biased slightly towards the smaller hoop).

## Two Throws 
```{r load in model for two throws, include = F, echo = F}
load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos")
load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos_draws")
```

```{r plotting for two throws, include = T, echo = F}
# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far")),
         Num_Throws = ifelse(Num_throws == "One_throw", "One", "Two")) %>% 
  ggplot(aes(prop, 
             colour = Num_Throws,
             fill = Num_Throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous("Normalised Delta") + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws"))

# plt_difference 
plt_difference <- draws$Plots[3][[1]] + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  guides(fill = guide_legend(title = "Distance"),
         colour = guide_legend(title = "Distance"))

# show this 
gridExtra::grid.arrange(plt_examples, plt_difference)
```

```{r Sort HDI, include = F, echo = F}
# get overall 
HDI_two_throw_overall_diff <- draws$HDIs[[2]]
HDI_two_throw_mean_pos_overall <- draws$HDIs[[1]]
mu <- HDI_two_throw_mean_pos_overall$mean
lower <- HDI_two_throw_mean_pos_overall$lower
upper <- HDI_two_throw_mean_pos_overall$upper

# get the closest 
HDI_tt_close <- draws$HDIs[[3]] %>% 
  filter(Dist_type == "Close")
mu_close <- HDI_tt_close$mean
lower_close <- HDI_tt_close$lower
upper_close <- HDI_tt_close$upper

HDI_tt_diff <- draws$HDIs[[4]]

P_close <- draws$Above_0[[2]] %>% 
  filter(Dist_type == "Close")
```
A Bayesian Beta regression was carried out to investigate whether participants performed the task in a more optimal way when they were given the chance to attempt to throw at both targets. The predictors were the No. of throws and Delta (Hoop separation). The predicted value was the normalised standing position with 0 being central and 1 being next to one of the hoops. 
The analysis suggested that there was an overall greater tendency for participants in the One-throw condition to stand further from the centre (mean of `r round(mu[1], digits = 3)`, 95% HPDI of |`r round(lower[1], digits = 3)` , `r round(upper[1], digits = 3)`|) than when they were in the Two-throw condition (mean of `r round(mu[2], digits = 3)`, 95% HPDI of |`r round(lower[2], digits = 3)` , `r round(upper[2], digits = 3)`|) with P(One-throw > Two-throw|data) = `r paste(round(draws$Above_0[[1]], digits = 3)*100, "%", sep = "")`.

As can be seen in the above figure, this effect was the strongest for the closest separation which reflects the larger amount of variation in standing position with distance in the Two-throw condition. In general, when in the One-throw condition, participants stood further from the centre (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) than in the the Two-throw condition (mean of `r round(mu_close[1], digits = 3)`, 95% HPDI of |`r round(lower_close[1], digits = 3)` , `r round(upper_close[1], digits = 3)`|) with P(One-throw > Two_throw|data) = `r paste(P_close$above0*100, "%", sep = "")`.

## Reward
```{r load in gambling data, include = F, echo = F, warning = F}
load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri")
load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri_draws")
draws_df <- draws_df %>% 
  mutate(prop = boot::inv.logit(estimate))

```{r make some plots, echo = F, inlude = T, warning = F}
# make separate plots for main effects and interactions 
plt_dist <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Dist_Type,
             fill = Dist_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Distance Type"),
         fill = guide_legend(title = "Distance Type")) +
  scale_x_continuous("Normalised Position")

plt_gamble <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous("Normalised Position")

plt_inter <- draws_df %>%
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous("Normalised Position") + 
  facet_wrap(~Dist_Type)

gridExtra::grid.arrange(plt_dist, plt_gamble, plt_inter)

>>>>

# Power Analysis

Our power analysis made use of simulations and resampling approaches based on data that we previously collected. Resampling was carried out in order to establish if adding more pariticipants to our sample sizes would have lead to a reduction in uncertainty around our estimates.

## Experiment 1: Two Hoop Sizes

We started by fitting a a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the `fitdistrplus` package. We then investigated how well we could detect various effects, and how this varied based on the sample size.

We altered the mean value but kept the variance the same to simulate participants shifting in one direction or the other. As can be seen in the figure below, we tested $X \in \{5\%, 10\%, 15\%, 20\%\}$ which were indicative of participants standing $X\%$ closer to the smaller hoop. These distributions were sampled from 5000 times by simulating $N = 3\ldots 24$ participants and 72 trials.

```{r load data and draw distributions, include = T, echo = F, fig.height = 3}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

# draw these 
df_distributions <- tibble(x_vals = rep(x, length(c(0,mu2))),
                           base = mu1,
                           diff = rep(c(0,mu2), each = length(x)),
                           var = var1,
                           alpha = get_shape_beta(base + diff, var)$alpha,
                           beta = get_shape_beta(base + diff, var)$beta,
                           est_mu = mu_beta(alpha, beta),
                           est_var = var_beta(alpha, beta),
                           p = dbeta(x_vals, alpha, beta))

df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p,
             colour = diff)) + 
  geom_line() + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")
```

The plot below the distributions shows the uncertainty surrounding the mean estimate for the smallest difference tested (5\%). After 15 participants, the uncertainty surrounding the estimate appears to plateau which demonstrates that the sample size of 21 was sufficient to detect the effect.

```{r  include = T, echo = F, fig.height = 3}

df_sample %>% 
  filter(difference == 0.05) %>% 
  group_by(n_subs) %>% 
  mutate(diff = comparison - baseline) %>% 
  summarise(mu = mean(diff), 
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) + 
  scale_x_continuous("Sample Size") + 
  theme_bw() + 
  theme(axis.title.y = element_blank())

## Experiment 2 and 3: Two Throws and Reward
As the hypothesis for both of these experiments was that out intervention would push participants towards being more optimal, we can use the same datasets to look at how uncertainty around the difference would change with varying sample sizes. For these experiments, comparison data was drawn from two unpublished studies; one in which the standard behaviour was observed, and one in which participants were closer to optimal in their performance.

@@

# Session Info

```{r}
sessionInfo()
```
